Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-22 manuscript/manuscript.Rmd
Move plot tangent space function into package

coords <- gpagen(format_for_gpagen(df), ShowPlot=F)$coords

real_plot_tangent_space <- function(coords, axis1="PC1", axis2="PC2") {
  x <- two.d.array(coords)
  pc.res <- prcomp(x)
  pcdata <- pc.res$x

	res <- as.data.frame(pcdata)
	res$id <- rownames(res)
	res2 <- res %>% separate(id, into=c("family", "role","sha"), sep="_") %>% tbl_df()

	# consensus in Procrustes space for downstream highlighting
	dots <- list(
		x=lazyeval::interp(~median(axis1, na.rm=T), axis1=as.name(axis1)),
		y=lazyeval::interp(~median(axis2, na.rm=T), axis2=as.name(axis2)))
	consensus <- res2 %>% group_by(family, role) %>% summarise_(.dots=dots)

	p <- ggplot(res2, aes_string(axis1, axis2, group="family")) + geom_point(aes(col=family, shape=role)) + geom_point(aes(x, y), data=consensus, alpha=0.5, size=5, col="black") + geom_point(aes(x, y, col=family, shape=role), data=consensus) + stat_ellipse(aes(color=family), linetype=2, type="norm", level=0.95) + theme_minimal() + theme(legend.position="none")

	direct.label(p, method="smart.grid")
}

real_plot_tangent_space(coords, "PC1", "PC2")
```

@@

```{r turker_morph_procrustes_other_pc34, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
real_plot_tangent_space(coords, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc56, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC5 and PC6 for turker / morphologist Procrustes space"}
real_plot_tangent_space(coords, "PC5", "PC6")
```

>>>>

coords <- gpagen(format_for_gpagen(df), ShowPlot=F)$coords
```

Text text

```{r turk_morph_procrustes_space, echo=FALSE, fig.cap="Testing my figure", anchor="figure"}
plot_tangent_space(coords, "PC1", "PC2")
```

Post text

@@

```{r turker_morph_procrustes_other_pc23, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC2 and PC3 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC2", "PC3")
```

```{r turker_morph_procrustes_other_pc34, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc45, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC4 and PC5 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC4", "PC5")
```
